### 2024-03-20 paper/main.tex

\section*{\raggedright
Another formula for the area of a triangle: \\
Useless, but explicitly in Deep-Sets and map--reduce form}
\noindent \textbf{David W. Hogg} and \textbf{Soledad Villar}

\paragraph{Abstract:}
It is known that any permutation-invariant function of data points $r_i$
can be written in the form $\rho(\sum_i\phi(r_i))$,
where $\rho$ and $\phi$ are (probably nonlinear) functions, and the function $\phi$ might output a high-dimensional latent encoding of each point $r_i$.
This form---known in the machine-learning literature as Deep Sets---is a map--reduce form, because the $\phi$ executions can be performed asynchronously and the sums can be performed hierarchically or in any order.
The area of a triangle is a permutation-invariant function of the locations of the three corners.
We find, possibly for the first time, the formula for the area of a triangle, given the positions of the three corners, that is explicitly in the Deep-Sets form.
It is the square-root of a quartic permutation-invariant polynomial.
No insights of any kind were gained by this work.

@@

A few comments about this Deep-Sets form \eqref{eq:DeepSets} we'd make are the following:
\begin{itemize}
    \item The function $\phi$ is universal to all the points $r_i$; it's form won't depend on any properties of each point, nor any properties of the overall collection of points (the \emph{point cloud}, as it were).
    \item The point properties $r_i$ and the output of the function $\phi$ might both be very large.
    That is, each point $r_i$ might be a vector or even an ordered list of vectors and tensors and images and so on, and the output of the function $\phi$ might also be very large and complicated.
    The output of the function $\phi$ is some kind of informative, latent encoding of the point $r_i$.
    \item If a function can be written in Deep-Sets form \eqref{eq:DeepSets}, then that function can be executed in a map--reduce framework, in which the function $\phi$ is executed independently and asynchronously on each data point (maybe even in the data center) and the sums are performed hierarchically or in any order.
    That means that for large problems executed on large data sets in large data centers, problems in this form \eqref{eq:DeepSets} can be performed in wall-clock time that scales as $\log N$.
\end{itemize}

>>>>

\section*{\raggedright
Another formula for the area of a triangle: Useless, but explicitly in Deep Sets and map--reduce form}

\noindent \textbf{David W. Hogg} and \textbf{Soledad Villar}

\paragraph{Abstract:}
It is known that any permutation-invariant function of data points $r_i$
can be written in the form $\rho(\sum_i\phi(r_i))$,
where $\rho$ and $\phi$ are (probably nonlinear) functions, and the function $\phi$ might output a high-dimensional latent encoding of each point $r_i$.
This form---known in the machine-learning literature as Deep Sets---is a map--reduce form, because the $\phi$ executions can be performed asynchronously and the sums can be performed hierarchically or in any order.
The area of a triangle is a permutation-invariant function of the locations of the three corners.
We find, possibly for the first time, the formula for the area of a triangle, given the positions of the three corners, that is explicitly in the Deep Sets form.
It is the square-root of a quartic permutation-invariant polynomial.
No insights of any kind were gained by this work.

@@

A few comments about this Deep Sets form \eqref{eq:DeepSets} we'd make are the following:
\begin{itemize}
    \item The function $\phi$ is universal to all the points $r_i$; its form won't depend on any properties of each point, nor any properties of the overall collection of points (the \emph{point cloud}, as it were).
    \item The point properties $r_i$ and the output of the function $\phi$ might both be very large.
    That is, each point $r_i$ might be a vector or even an ordered list of vectors and tensors and images and so on, and the output of the function $\phi$ might also be very large and complicated.
    The output of the function $\phi$ is some kind of informative, latent encoding of the point $r_i$.
    \item If a function can be written in Deep-Sets form \eqref{eq:DeepSets}, then that function can be executed in a map--reduce framework, in which the function $\phi$ is executed independently and asynchronously on each data point (maybe even in the data center) and the sums are performed hierarchically or in any order.
    That means that for large problems executed on large data sets in large data centers, problems in this form \eqref{eq:DeepSets} can be performed in wall-clock time that scales as $\log N$.
\end{itemize}
